\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[preprint]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

% Additional packages
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage{multirow}
\usepackage{stfloats}

% If the title and author information does not fit in the area allocated, uncomment the following
%\setlength\titlebox{<dim>}

\author{
 \textbf{Bingxi Zhao\textsuperscript{1,2}$^*$},
 \textbf{Jiahao Zhang\textsuperscript{1}$^*$},
 \textbf{Xubin Ren\textsuperscript{1}},
 \textbf{Zirui Guo\textsuperscript{1}},
 \textbf{Chao Huang\textsuperscript{1}$^\dagger$}
\\
 \textsuperscript{1}University of Hong Kong,
 \textsuperscript{2}Beijing Jiaotong University,
\\
 \small{
   \textbf{Correspondence: \{bingxizhao39, chaohuang75\}@gmail.com} 
 }
}

\begin{document}
\title{DeepTutor: Tool-Augmented Personalized Tutoring System}
\maketitle

\begin{abstract}
\renewcommand{\thefootnote}{}%
\footnotetext{\hspace{-1.8em}$^*$Equal contribution.\newline $^\dagger$Corresponding author.}%
\renewcommand{\thefootnote}{\arabic{footnote}}%
\setcounter{footnote}{0}%
Education is among the most promising real-world applications of large language models (LLMs). 
While current LLMs exhibit strong abilities, they rely heavily on static knowledge acquired during pre-training stages.
While current RAG systems can anchor responses in course
content, they optimize for retrieval precision rather than the adaptive,
guided explanations that effective tutoring demands.
In this paper, we present \textsc{DeepTutor}, among the first open-source agentic frameworks to unify citation-grounded problem-solving and difficulty-calibrated question generation.
These two capabilities are unified through a hybrid personalization engine that couples static knowledge grounding with a trace forest that continuously refines an evolving learner profile to customize every interaction.
To further evaluate personalized tutoring abilities, we construct TutorBench, a benchmark containing 100 KB-grounded learner profiles to perform first-person interactive assessments via profile-driven student simulator. 
Generalization experiments on five standard benchmarks further show that our reasoning pipeline lifts solving accuracy by approximately 25\% on average over the backbone model across these datasets. 
\textsc{DeepTutor} system with full evaluation suites are open-sourced at \url{https://github.com/HKUDS/DeepTutor/tree/eval}.

\end{abstract}

% ===== Sections =====
\input{sections/intro}
\input{sections/method}
\input{sections/experiments}
\input{sections/related-work}
\input{sections/conclusion}
\input{sections/limitation}

\section*{Acknowledgments}

% Bibliography
\bibliography{custom}

\appendix
\input{sections/appendix}

\end{document}
